---
title: "Kaggle R Notebook"
output: html_notebook
---

Stuff for convenience.

```{r}
PRIM_TYPES <- c("integer", "double", "character", "logical", "complex", "raw")

```

Data exploration of Kaggle run.

```{r}
library(tidyverse)
```

Load data.

```{r}
# df <- read_csv("/mnt/nvme0/R/project-typeR/artifact/typeR/kaggle/kaggle-run/assertions-all.csv")
df <- read_csv("../data/all-assertions-kaggle.csv")

df_failed <- df %>% filter(!assertion_status)

df_failed_no_undef <- df_failed %>% filter(expected_type != "<undefined>")
```

How many failed assertions were there?

```{r}
perc_failed <- (df %>% filter(!assertion_status) %>% nrow) / (df %>% nrow)

perc_failed
```

This is in line with what we found for the reverse dependency test.
What if we look at the same breakdowns that we did with the failed assertions for the rev deps test?

```{r}
df_failed_assertions_summarized <- df_failed_no_undef %>% group_by(expected_type, actual_type) %>% summarize(num = n()) %>% arrange(-num) %>% ungroup

# First one:
df_failed_assertions_summarized %>% slice(1)
```

```{r}
df_failed %>% filter(expected_type == "class<`matrix`>", actual_type == "class<data.table, data.frame>") %>% unique
```

One example: we have matrices being passed to data.frames.
Let's look at the function, in this case, `class::knn`:

```{r}
# > class::knn
# function (train, test, cl, k = 1, l = 0, prob = FALSE, use.all = TRUE) 
# {
#     train <- as.matrix(train)
#     if (is.null(dim(test))) 
#         dim(test) <- c(1, length(test))
#     test <- as.matrix(test)
#     ...
# }
```

We see that the first two arguments (which are the ones with failing contracts) are immediately converted to matrices, though this function was only ever tested with matrix arguments.
A better type here would be one that's "convertible to a matrix".

More:

```{r}
df_failed %>% filter(expected_type == "^character[]", actual_type == "class<factor>") %>% unique 
```

The two functions, `stringr::str_detect` and `stringr::str_extract` were tested with characters only, but they do also operate on factors, likely because they ignore the class of the passed value.

More:

```{r}
df_failed %>% filter(expected_type == "list<integer[]> | list<list<any>> | list<class<`function`>> | list<class<`function`> | class<`function`, `purrr_function_compose`>> | list<class<`function`> | class<`formula`>> | list<class<`function`> | class<`function`, `rlang_lambda_function`>> | list<class<`formula`>> | double[] | list<character | double> | list<class<`lm`>> | list<class<`data.frame`>> | class<`data.frame`, `tbl`, `tbl_df`> | class<`data.frame`> | list<class<`formula`, `quosure`>>", actual_type == "character[]") %>% unique 
```

This is probably a bug?

```{r}
df_failed %>% filter(expected_type == "double[]", actual_type == "integer[]") %>% unique 
```

```{r}
df_failed %>% filter(expected_type == "list<integer[]> | list<list<any>> | list<class<`function`>> | list<class<`function`> | class<`function`, `purrr_function_compose`>> | list<class<`function`> | class<`formula`>> | list<class<`function`> | class<`function`, `rlang_lambda_function`>> | list<class<`formula`>> | double[] | list<character | double> | list<class<`lm`>> | list<class<`data.frame`>> | class<`data.frame`, `tbl`, `tbl_df`> | class<`data.frame`> | list<class<`formula`, `quosure`>>", actual_type == "character[]") %>% unique 
```

This reveals `purrr::map`, which does work on character[]-types values.
However, it was only ever tested with list-typed values.

Ok. How often are we passing vectors to scalars?

```{r}
df_failed_no_undef %>% filter(expected_type %in% c(PRIM_TYPES, paste0("^", PRIM_TYPES)), actual_type %in% c(paste0(PRIM_TYPES, "[]"), paste0("^", PRIM_TYPES, "[]"))) %>% select(package_name, function_name, parameter_position, actual_type, expected_type) %>% unique
```

`lattice:::trellis.device` and `lattice:::canonical.theme` look like errors in Kaggle. `readr:::output_column` is a multi method, and only one of the implementations were probably tried (`readr:::output_column.default`), whereas this probably tests `readr:::output_column.double`.

What about things that expect classes?

```{r}
df_failed_no_undef %>% filter(str_detect(expected_type, "class")) %>% select(package_name, function_name, parameter_position, actual_type, expected_type) %>% unique
```

`e1071:::tune`'s `train.y` argument can take a data.frame, and the function converts it if passed, it's just that it wasnt tested.
`dplyr:::if_else` should be any typed in 2nd and 3rd arg.
`dplyr:::inner_join` is a limitation of our approach (gets a data.frame, asks for a data.frame+tbl+tbl_df).

```{r}

```


